%\vspace{-0.1in}
\section{Curriculum Development Activities}

%This section describes the work we plan to do in both integrating the research
%described in this proposal into education and also broadening participation in
%computer science. 
%The CS Department at FSU is strengthening its parallel computing
%curriculum. The PI developed a new introduction to parallel computing
%course offered to undergraduate students in Fall 2011. 

PI Yuan is an early adopter funded for curricular 
development under the NSF/TCPP initiative for parallel and distributed
computing~\cite{TCPP}.
Both Lowenthal and Yuan have developed and offered 
a sequence of two parallel computing courses: an introduction to
parallel computing course (at the undergraduate and graduate levels)
and an advanced topics graduate course in
Parallel and Distributed Systems.
This project will greatly enhance these courses.
The PIs will work together to develop projects and educational modules
in job scheduling, resource management, and software-defined networking
for use in courses at UA and FSU.

Specifically, at the undergraduate level, 
Yuan will integrate the software-defined networking
module, and Lowenthal will integrate the job scheduling module, into
their respective parallel and distributed systems courses.
%Lowenthal covered such a unit
%in the most recent offering of the course, but he will extend it with
%the scheduling material in this proposal the next time he offers the
%course.
Both PIs will assess and improve the modules and then
eventually adopt both.

\iffalse
At the graduate level, the PIs will jointly develop a relevant set of
papers that cover the key topics presented in the proposal (job
scheduling, resource management, network contention, SDN).  These
papers will
be combined with a large project that will be based on the HPC\_SDN
system described in this proposal.  Specifically, graduate students
will add features to our system as part of their term project.  One
example would be the development of static analysis to obtain
application-level information to be passed to HPC\_SDN---this is not
covered in our proposal, but would be itself an interesting line of
work.
\fi

At the graduate level, the PIs will jointly develop a relevant set of
papers and projects that cover the key topics presented in the proposal (job
scheduling, resource management, network contention, SDN).
%These
%papers will
%be combined with a large project that will be based on the HPC\_SDN
%system described in this proposal.
Specifically, graduate students
will add features to our HPC\_SDN system as part of their term project.  One
example project would be the development of static analysis to obtain 
application-level information to be passed to HPC\_SDN.
%---this is not
%covered in our proposal, but would be itself an interesting line of
%work.

\iffalse
For the advanced topics course, Yuan plan to introduce a number of
course project topics on job scheduling, resource management, and SDN 
based on the research in the project. Additionally, he will
cover relevant papers and work (jointly with Lowenthal) towards the
development of a project that will teach students the benefits of
SDN and job scheduling.
\fi



